A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)

### 2018-04-14 Papers/AppliedMaths2018/Stochastic_Upscaling_UK_AMM_2018.tex
updates

\medskip
Figure~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} presents snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases. Figure~\ref{fig:BaseCase_Saturation}, \ref{fig:ArithMeanCase_Saturation}, \ref{fig:HarmMeanCase_Saturation}, \ref{fig:PDFCase_Saturation}, \ref{fig:SVDCase_Saturation} show the simulation for the BaseCase, ArithMeanCase, HarmMeanCase, PDFCase and SVDCase, respectively. In Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation}  (c) shows that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (d) and (e)). Fig.~\ref{fig:BaseCase_Saturation} - \ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.

Fig.~\ref{fig:Saturationfield@t=1.15s} compares the phase 1 saturation field for all the cases at $t=1.15s$. Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical. Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c). This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean. However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ . Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistence is with respect to this realization of the PDFCase. Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)

>>>>

\medskip
\red{(I GUESS YOU SHOULD USE ONE PARAGRAPH JUST TO DESCRIBE (TO THE READER WHO HASNT READ THE OTHER REFERENCES) THE PHYSICS ASSOCIATED WITH THE BASECASE -- FIG 4 LINKING WITH THE REFERENCES ... REMEMBER THIS IS YOUR WORK'S VALIDATION!!! THIS BENCHMARK WOULD: (A) IF THE SIMULATION WAS PERFORMED W HOMOGENEOUS MEDIA (AT EACH BLOCK) A PISTON SHAPE BEHAVIOR (AT EACH BLOCK, I.E., A BLOCK DIVIDED BUCKLEY-LEVERETT BEHAVIOR) COULD BE NOTICED HOWEVER AS THE WHOLE SYSTEM IS HETEROGENEOUS THIS MAY NOT BE CLEARLY NOTICED; (B) CROSS-FLOW, I.E., PREFERENTIAL FLOW  THROUGH REGIONS OF HIGH PERMEABILITY; (C) FLOW QUALITATIVE BEHAVIOUR MATCHES THE EXPERIMENTS  ETC ETC ETC MAKE IT STRONG !)}

Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} show snapshots of phase 1 (\ie injected or displacing fluid) saturation field for all studied cases. In Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation}(a) and (b), even though fluid is injected at the same rate across the left face it travels faster in $K1$ compared to $K2$. Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (c) show that fluid experience a resistance to flow at the interface between $K1$ and $K3$ which encourages the flow into $K4$ (Figs.~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (d) and (e)). Figures~\ref{fig:BaseCase_Saturation}-\ref{fig:SVDCase_Saturation} (f) indicates preferential flow in $K4$ compared to $K3$.

Figure~\ref{fig:Saturationfield@t=1.15s} compares phase 1 saturation distribution for all the cases at $t=1.15s$. Generally, the simulations closely resemble each other with the simulation in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c) being the most identical. Albeit, closer inspection will reveal that there is more injection in Fig.~\ref{fig:Saturationfield@t=1.15s}(b) compared to (c). This is logical giving that the block mean values calculated for arithmetric mean is higher than that for harmonic mean. However, the important feature of the figures (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(b) and (c)) is that they poorly represent the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) at the top left hand corner of block $K2$ . Fig.~\ref{fig:Saturationfield@t=1.15s}(d) also shows an inconsistency with the BaseCase (\ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)) where it shows phase 1 moving from block $K2$ into $K4$. This inconsistence is with respect to this realization of the PDFCase. Hence, by elimination the SVDCase in Fig.~\ref{fig:Saturationfield@t=1.15s}(e) give the best representation of the BaseCase in \ie Fig.~\ref{fig:Saturationfield@t=1.15s}(a)

### 2018-04-14 Papers/AppliedMaths2018/article_figure1.tex
updates

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{\hspace{0.5cm} (a) BaseCase(with mesh) \hspace{3.75cm} (b) BaseCase(without Mesh) \hspace{3.0cm} (c) ArithMean Case}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_PermField_withoutMesh2.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{ \hspace{1.5cm} (d) HarmMean Case \hspace{4.75cm} (e) PDFCase  \hspace{5.0cm} (f) SVDCase}
\vspace{0.cm}
}   
\caption{Permeability field for the base case as well as the upscaled cases}
\label{fig:PermFields}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\hspace{4cm} \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15withlegend.png}
      \hspace {1.5cm} \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot15.png}}
\vspace{0.cm}
\hbox{\hspace{3.75cm} (a) BaseCase: Phase 1 Saturation at t=1.15s \hspace{1cm} (b) ArithMeanCase: Phase 1 Saturation at t=1.15s}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_1dot15.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_1dot15.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_1dot15.png}}
\vspace{0.cm}
\hbox{ \hspace{0cm} (c) HarmMeanCase: Saturation (t=1.15s) \hspace{0.5cm} (d) PDFCase: Saturation (t=1.15s) \hspace{1.5cm} (e) SVDCase: Saturation (t=1.15s)}
\vspace{0.cm}
}   
\caption{Comparing the phase 1 saturation field for all the models at t=1.15s}
\label{fig:Saturationfield@t=1.15s}
\end{figure}
\end{landscape}
\clearpage

>>>>

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withMesh.png}
      \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{\hspace{0.5cm} (a) BaseCase (overlapped with the mesh) \hspace{3.75cm} (b) BaseCase (without Mesh) \hspace{3.0cm} (c) ArithMean Case}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_PermField_withoutMesh2.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_PermField_withoutMesh2.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_PermField_withoutMesh2.png}}
\vspace{0.cm}
\hbox{ \hspace{1.5cm} (d) HarmMean Case \hspace{4.75cm} (e) PDFCase  \hspace{5.0cm} (f) SVDCase}
\vspace{0.cm}
}   
\caption{Permeability field for the base case as well as the upscaled cases}
\label{fig:PermFields}
\end{figure}
\end{landscape}
\clearpage

@@

%%%%
%%%%  FIGURE
%%%%
\begin{landscape}
\begin{figure}[ht] 
\vbox{\vspace{-1cm}
\hbox{\hspace{4cm} \includegraphics[width=.56\textwidth]{./Pics/BaseCase/BaseCase_Saturation_t_1dot15withlegend.png}
      \hspace {1.5cm} \includegraphics[width=.56\textwidth]{./Pics/ArithMeanCase/ArithMeanCase_Saturation_t_1dot15.png}}
\vspace{0.cm}
\hbox{\hspace{3.75cm} (a) BaseCase\hspace{1cm} (b) ArithMeanCase}
\vspace{0.5cm}
\hbox{
      \includegraphics[width=.56\textwidth]{./Pics/HarmMeanCase/HarmMeanCase_Saturation_t_1dot15.png}
      \includegraphics[width=.56\textwidth]{./Pics/PDFCase/PDFCase_Saturation_t_1dot15.png} 
      \includegraphics[width=.56\textwidth]{./Pics/SVDCase/SVDCase_Saturation_t_1dot15.png}}
\vspace{0.cm}
\hbox{ \hspace{0cm} (c) HarmMeanCase \hspace{0.5cm} (d) PDFCase \hspace{1.5cm} (e) SVDCase}
\vspace{0.cm}
}   
\caption{Comparing phase 1 saturation distribution for all the models at $t=1.15$ s}
\label{fig:Saturationfield@t=1.15s}
\end{figure}
\end{landscape}
\clearpage
